### 2016-12-05 local-capability-machine.tex
first version of assembly awkward example

\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{thmtools}
\usepackage{stmaryrd}
\usepackage{natbib}
\usepackage{url}
\usepackage{array}
\usepackage{arydshln}
\usepackage{ifthen}
\usepackage{ifpdf}
\usepackage{verbatim}
\usepackage{mathpartir}

@@

The stack resides entirely in memory. There is no separation between the memory and the stack, so when we talk about the stack it is as a conceptual thing.

@@

\item[\texttt{load $r$ $x$}] Assumes environment capability available in register $r_{\var{env}}$. Loads the at the index associated with $x$ in the list. Loads from this capability into $r$.
\item[\texttt{store $x$ $r$}] Assumes environment capability available in register $r_{\var{env}}$. Loads the at the index associated with $x$ in the list. Stores the contents of register $r$ through this capability.

@@

\subsection{Variant of the ``awkward'' example}
Assembly variant of the ``awkward'' example from \citep[p.~11]{Dreyer:2010:IHS:1863543.1863566}. 
\begin{verbatim}
g = fun _ => let x = 0 in
               fun f =>
                 x := 0;
                 f();
                 x := 1;
                 f();
                 assert(x == 1)
\end{verbatim}

>>>>

\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{thmtools}
\usepackage{stmaryrd}
\usepackage{natbib}
\usepackage{url}
\usepackage{array}
\usepackage{arydshln}
\usepackage{ifthen}
\usepackage{ifpdf}
\usepackage{verbatim}
\usepackage{mathpartir}
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily,
  columns=fullflexible,
  keepspaces=true,
  mathescape
}

@@

The stack resides entirely in memory. There is no separation between the memory and the stack, so when we talk about the stack it is as a conceptual thing. %

@@

\item[\texttt{load $r$ $x$}] Assumes environment capability available in register $r_{\var{env}}$. Loads the word at the index associated with $x$ in the environment list. Loads from this capability into $r$.
\item[\texttt{store $x$ $r$}] Assumes environment capability available in register $r_{\var{env}}$. Loads the word at the index associated with $x$ in the environment list. Stores the contents of register $r$ through this capability.

@@

\subsection{Variant of the ``awkward'' example}
Assembly variant of the ``awkward'' example from \citep[p.~11]{Dreyer:2010:IHS:1863543.1863566}. 
\begin{verbatim}
g = fun _ => let x = 0 in
               fun f =>
                 x := 0;
                 f();
                 x := 1;
                 f();
                 assert(x == 1)
\end{verbatim}
\begin{lstlisting}
g2:  malloc $r_2$ 1
     store $r_2$ 0
     move $\pcreg$ $r_3$
     lea $r_3$  $\dots$
     crtcls $[(x, r_2)]$ $r_3$
     rclear $\RegName \setminus \{\pcreg,r_0,r_1 \}$
2g:  jmp $r_0$

f4:  reqglob $r1$
     reqperm $r_\stk$ $\encodePerm(\rwlx)$
     store $x$ 0
     scall $r_1$($[]$,$[r_0,r_1]$)
     store $x$ 1
     scall $r_1$($[]$,$[r_0]$)
     load $r_1$ x
     assert $r_1$ 1
     cclear $\RegName \setminus \{r_0,\pcreg\}$
4f:  jmp $r_0$
\end{lstlisting}
